Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-05-29 Paper.tex
changes to intro and fixes for images

\begin{wrapfigure}{r}{0.36\textwidth}
\vspace{-2em}\centering
  \fbox{
    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
    \caption{Straight Learning Path}\label{fig:straight}
    \vspace{5pt}  
      \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
      \vspace{-1.8em}
      \caption{Winding Learning Path}\label{fig:curvy}
      \vspace{-2em}
\end{wrapfigure}

Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you
know that it is hard to hike up a steep mountain directly as shown in
\autoref{fig:straight}. Some people do it but most people will rather hike up as shown in
\autoref{fig:curvy}. Both paths lead to the goal though. Within Mathematics classes, there
is normally only one straight path and this has not changed in decades. With the
advancement of technology, we are however able to change the way presentations and their
narratives work. We can make it possible to link content that logically belongs together,
in other words, content that is semantically close. Through the linking of content it
becomes possible for a presenter to seamlessly lead an audience, not along a predetermined
straight path, but rather along the path that allows the audience to take small detours
and ultimately make the most out of the presentation.\ednote{This intro does not work for
  math. Math instruction is mostly done via blackboard, and teachers can flexibly take any
  path they want with that in response to student understanding (or lack, ... ). Maybe we
  can turn this around: math uses blackboard, because it is flexible. Presentations are
  too inflexible for math, let's make them better.}

\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem_cropped}}\vspace{-.5em}
  \caption{Theorem Slide}\label{fig:slideP}
  \vspace{-15pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{.55\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.55\textwidth]{assets/final/Architecture}} 
  \vspace{-1em}
  \caption{Architecture Diagram}\label{fig:architecture}\vspace{-1em}
\end{wrapfigure}

@@

\begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \caption{Inclusion Graph for the Pythagorean Theorem}\label{fig:inclusionGraph}
\end{wrapfigure}

@@

\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
  \vspace{-2em}
\end{wrapfigure}
With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

\subsection{Levels}
\label{sec:levels}

\begin{wrapfigure}r{.63\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
  \vspace{-1em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-2em}
\end{wrapfigure}
When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.4\textwidth]{assets/final/60degree}} 
  \vspace{-.5em}
  \caption{Visualization of Dependencies and Levels at 60\degree}
  \label{fig:visualDependencyDegree}
\vspace{-1em}
\end{wrapfigure}
If Annie, while browsing through the different dependencies, realizes that she needs to
refresh her memory or learn more about any of the dependent information she can enter the
respective level. The presentation will then continue on that level and show all the
slides from that topic in the correct order. Once Annie has gone through this short
excursion, she can return to the initial slide and resume the primary narrative path. By
adding a way to explore these other levels, the presentation adds more context and allows
Annie to understand the subject on a deeper level. These modular excursions are included
in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
story line -- see \autoref{fig:visualDependencyDegree}. The overlapping slides do not
interfere as they are at a 90\degree\ angle. Therefore when seeing one slide, the other
slide will be visible only from the side. Since a slide is very thin this makes it
invisible.

>>>>

\begin{wrapfigure}{r}{0.38\textwidth}
\vspace{-2.1em}\centering
  \fbox{
    \includegraphics[width=0.37 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
    \caption{Straight Learning Path}\label{fig:straight}
    \vspace{5pt}  
      \fbox{\includegraphics[width=0.38 \textwidth]{assets/final/curvyMountain}}
      \vspace{-1.8em}
      \caption{Winding Learning Path}\label{fig:curvy}
      \vspace{-2.8em}
\end{wrapfigure}

Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you
know that it is hard to hike up a steep mountain directly as shown in
\autoref{fig:straight}. Some people do it but most people will rather hike up as shown in
\autoref{fig:curvy}. Both paths lead to the goal though. Within Mathematics classes, professors that teach using a blackboard have the ability to diverge from their teaching plan when needed. The lack of flexibility of slides might in fact be why the blackboard teaching approach prevails especially in Mathematics. Yet offline materials given to students such as slides, books, or other documents prescribe one straight path and this has not changed in decades. With the advancement of technology, we are however able to change the way classroom materials and their
narratives work. We can make it possible to link content that logically belongs together,
in other words, content that is semantically close. Through the linking of content it
becomes possible for a presenter to seamlessly lead an audience, not along a predetermined
straight path, but rather along the path that allows the audience to take small detours
and ultimately make the most out of the presentation.

\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem_cropped}}\vspace{-.5em}
  \caption{Theorem Slide}\label{fig:slideP}
  \vspace{-20pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{.55\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.53\textwidth]{assets/final/Architecture}} 
  \vspace{-1.7em}
  \caption{Architecture Diagram}\label{fig:architecture}
  \vspace{-1.5em}
\end{wrapfigure}

@@

\begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.63\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \vspace{-1.8em}
  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
  \vspace{-2em}
\end{wrapfigure}

@@

\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1.8em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
  \vspace{-2em}
\end{wrapfigure}
With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{The library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

\newpage
\subsection{Levels}
\label{sec:levels}

\begin{wrapfigure}r{.63\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
  \vspace{-0.8em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-2em}
\end{wrapfigure}
When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.41\textwidth]{assets/final/60degree}} 
  \vspace{-1.8em}
  \caption{Visualization of Dependencies and Levels at 60\degree}
  \label{fig:visualDependencyDegree}
\vspace{-1.8em}
\end{wrapfigure}
If Annie, while browsing through the different dependencies, realizes that she needs to
refresh her memory or learn more about any of the dependent information she can enter the
respective level. The presentation will then continue on that level and show all the
slides from that topic in the correct order. Once Annie has gone through this short
excursion, she can return to the initial slide and resume the primary narrative path. By
adding a way to explore these other levels, the presentation adds more context and allows
Annie to understand the subject on a deeper level. These modular excursions are included
in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
story line -- see \autoref{fig:visualDependencyDegree}. The overlapping slides do not
interfere as they are at a 90\degree\ angle. Therefore when seeing one slide, the other
slide will be visible only from the side. Since a slide is very thin this makes it
invisible.
